divan: An R Shiny app for exploratory functional diversity analyses

### 2023-11-02 paper/paper.Rmd
update metadata

---
title: 'divan: An R Shiny app for exploratory functional diversity analyses'
author:
- name: Facundo X. Palacio
  affiliation: 1, 2
  corresponding: yes
- name: "Caio Graco-Roza"
  affiliation: 3
- name: Emma J. Hudgins
  affiliation: 4
date: "2 November 2023"
affiliation:
- name: Sección Ornitología, Universidad Nacional de La Plata, Argentina
  index: 1
- name: Consejo Nacional de Investigaciones Científicas y Técnicas, Argentina
- index: 2
- name: University of Helsinki, Helsinki, Finland
  index: 3
- name: School of Agriculture, Food, and Ecosystem Sciences, The University of Melbourne,
    Australia
  index: 4
tags:
- Shiny
- functional ecology
- biodiversity
- functional traits
bibliography: paper.bib
output: md_document
---

>>>>

---
title: 'divan: An R Shiny app for exploratory functional diversity analyses'
authors:
- name: Facundo X. Palacio
  affiliation: 1, 2
  corresponding: yes
- name: "Caio Graco-Roza"
  affiliation: 3
- name: Emma J. Hudgins
  affiliation: 4
date: "2 November 2023"
affiliations:
- name: Sección Ornitología, Universidad Nacional de La Plata, Argentina
  index: 1
- name: Consejo Nacional de Investigaciones Científicas y Técnicas, Argentina
- index: 2
- name: University of Helsinki, Helsinki, Finland
  index: 3
- name: School of Agriculture, Food, and Ecosystem Sciences, The University of Melbourne,
    Australia
  index: 4
tags:
- Shiny
- functional ecology
- biodiversity
- functional traits
bibliography: paper.bib
output: md_document
---
